Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
How big are your graphs

For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
subgraph isomorphism \cite{thelionpaper}. This collection includes randomly generated scale-free
graphs \cite{constraints10}, an assortment of real-world graphs of varying sizes \cite{LV02},
randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
satisfiable), segmented images~\cite{pr15,cviu11}, meshes from modelling 3D objects \cite{cviu11},
and graphs close to the satisfiable-unsatisfiable phase transition
\cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.
Note that many of these instances are \emph{much} larger than were used in the recent comparison of
maximum common subgraph algorithms by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs,
they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
up to ?? vertices and targets with up to ?? vertices. For maximum common subgraph, 1,560 of the
instances cannot fit in the amount of RAM we have available---we treat these instances as having
timed out. The situation for the clique encoding is even worse, and 3,653 of these instances do not
fit in RAM. In contrast, for our algorithm, every instance fits comfortably (at least on modern
server-class hardware).

>>>>

For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
subgraph isomorphism \cite{thelionpaper}. This collection includes randomly generated scale-free
graphs \cite{constraints10}, an assortment of real-world graphs of varying sizes \cite{LV02},
randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
satisfiable), segmented images~\cite{pr15,cviu11}, meshes from modelling 3D objects \cite{cviu11},
and graphs close to the satisfiable-unsatisfiable phase transition
\cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the CP
algorithm, 1,560 of the instances cannot fit in the amount of RAM we have available---we treat these
instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
these instances do not fit in RAM. In contrast, for our algorithm, every instance fits comfortably
(at least on modern server-class hardware).
